\section{1N}

\subsection{response}

A brief summarize table: \\[1em]
{\small\ttfamily
\begin{NiceTabular}{ccccc}[hvlines]
    & s/o & inv & CoG & SI+ \\
4M (6m poss.) &                  & 2C->raise/2N   & 2C                 & 2C-2M-3oM/spl \\
5M            & \Block{2-1}{2DH} & 2D->2N; 2C->2S & 2DH->3m/3N; 2H->2N & 2D->3m; 2H->2N/3m \\
6M            &                  & 2DH->raise     & (4DH is s/o)       & 2DH->4M (MST); 2DH->3oM+ \\
5S4H          & \Block{3-1}{2C->P/2H} & 2C->2S/3H & \Block{3-1}{Smolen (2C-2D-3HS)} & \Block{2-1}{Smolen} \\
5H4S          &                  & 2D->2S         &                    &  \\
55+M          &                  & 2H->3H         &                    & 4C \\
64M           & 2DH              & be 6M or 54M   & 2C-2D-4CD          & 2C-2D-4CD \\
6m            & 2S/3C            & 2S/3D          & 2S/3C->3N/bid(spl) & 2S/3C->raise/4N/bid(spl) \\
\end{NiceTabular}
}

\input{\currfiledir/seq/resp}

\subsubsection{After Stayman}
\input{\currfiledir/seq/Stayman}

\subsubsection{After transfer}
\input{\currfiledir/seq/after_transfer}

\subsection{comp}

\subsubsection{doubled}

We use similar structure against double. However, knowing some weaknesses may help:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item If the opponent lacks PEN X, try P with boring hands NV (even with medium-quality 5M suit)
    \item For X/bids shows an ambiguous suit, we may try to interfere with overcall
    \item After XX, we set up FP. Either one's X means "if you hold Hx+, please PEN"; 2N shows a t/o hand if FP ON.
    \item Notice about our escape scheme:
        \begin{itemize}
            \setlength\itemsep{0pt}
            \item If X = PEN, then direct bid is s/o
            \item Otherwise, system on
            \item P transfers to XX, but since it usually denies inv values (can still have some bad 8-9 that is not willing to FP), opener can freely bid his 5-card suit.
            \item No matter what X means, after P transfer to XX, a bid is "DONT" style, and resp can also pass.
        \end{itemize}
\end{itemize}

\bin{\currfiledir/seq/1N-X}

\subsubsection{2m = majors}

We use a simple structure against 2m = majors.

\input{\currfiledir/seq/2m_MM}

\subsection{2C = some 6+}

\texttt{X = (s)bal inv+, FP ON}, \texttt{2X = NF}. Leb ON.

\subsection{other natrual bids (even if promises another suit)}

\texttt{X = t/o}, \texttt{2X = NF}. Leb ON.

\subsection{note on FP}

If FP ON, and before giving up PEN, \texttt{2N = t/o, min, NF}, suit = 4+ card (unlikely to have 5-card)
