\section{uncontested 1X}

\subsection{1m}

\begin{itemize}
    \setlength\itemsep{0pt}
    \item transfer response to 1C
    \item 2H = reverse Flannery
    \item some art minor raises. non-inverted minors
\end{itemize}
\bin{\currfiledir/seq/1m}

\subsection{1M}

\begin{itemize}
    \setlength\itemsep{0pt}
    \item 3m = inv
    \item we play Kaplan-interchange after 1H, i.e. \texttt{1N = 5+S, 1S = 4-S}
    \item however, 6+S inv will bid 1S initially, then rebid 2S regardless of opener's rebid.
\end{itemize}
\bin{\currfiledir/seq/1M_}

\subsubsection{PH}

\bin{\currfiledir/seq/1M_PH}

\subsection{Gazzilli}

Let's introduce the concept of Gazzilli before rebid: the traditional Gazilli applies to \texttt{1H - 1SN - 2C \& 1S - 1N - 2C}: which shows either 16+ or 6+M.
For response, \texttt{2D} is artificial, F1 that shows 8+ (GF against 16); while other bids are 7- and natrual. 
The only exception are limit raise, \texttt{1H - 1S; 2C - 2S = 6+S inv}, and \texttt{1S - 1N; 2C - 3H = 1-S, 6+H inv}.
(side note: for weak hand, usually bid 2M with 2+M (or even 1M if no good suit). otherwise, bid 2H/3m. 2N = mms.)
The main advantages are:
\begin{itemize}
    \setlength\itemsep{0pt}
    \item free up spaces for shapely hands
    \item 6+M GF hands can now bid 2C first (1M - 1N - 3M still 15-17 6+M or weaker with longer M)
\end{itemize}

For minor opening, Thanks to transfer response \& unbal 1D, \texttt{1C - 1DH - 1S \& 1D - 1M - 1N} are empty.
Notice that these are very suitable for Gazzilli, since it is a two-under bid for 2m. 
Therefore, we similarly define it to be either 16+ or weak unbal (i.e. the natrual 1m - 1M - 2m).
The responses are similar: 

\begin{itemize}
    \setlength\itemsep{0pt}
    \item +1 = art, 8+ (except the following) and others are nat and weak (2N ?)
    \item since \texttt{1m - 2H = 3-7 reverse Flannery}, \texttt{1D - 1S - 1N - 2H \& 1C - 1H - 1S - 2H} shows 8-10, 5S4H+
    \item others = (absolute) s/o
\end{itemize}

\subsubsection{opener's 1m - 1M plan in brief}

other unmentioned bids are quite natrual.

\begin{itemize}
    \setlength\itemsep{0pt}
    \item 4+M fit $\to$ always show first. (note: the only fit we won't show first round is GF fit after \texttt{1H - 1N*})
    \item 4+M fit min bal $\to$ \texttt{1C - 1DH* - 2M}
    \item 4+M fit min unbal (11-13(14) w/ short or 11-16 5m4M22) $\to$ \texttt{1C - 1DH* - 2D*} and \texttt{1D - 1M - 2M} (15-16 5m4M22 promises rebid)
    \item 4+M fit mid+ spl (good 14+) $\to$ new suit between 2M \~ 3M are minispl. \texttt{1D - 1M - [lowest minispl]} may be 15-16 5M4m22 (ask with +1 --- back to 3M = 5M4m22)
    \item \texttt{1m - 1M - 2m = (13)14-15, good 6m, 0-3M}
    \item \texttt{1m - 1M - 3m = (15)16-17, good 6m, 0-2M}
    \item all other unbal goes to Gaz, then ...
    \item if Gazzilli accepted (\texttt{... Gaz - Gaz+1}), then back to 2m (2-M or sometimes 6+m) and 2M (3M fit) shows min unbal.
    \item if Gazzilli accepted (\texttt{... Gaz - Gaz+1}), boring 16+ hands just simply use \textit{the waiting bid}. otherwise, other bids usually shows shapely and slam interest.
    \item if Gazzilli not accepted and 2M available, back to 2M shows (15)16-17, good 6m-3M. (ex: \texttt{1C - 1D; 1S - 2D; 2H}) jump 3M = GF, good 6m-3M.
    \item if Gazzilli not accepted and resp back to 2M, raise 3M = inv
    \item if Gazzilli not accepted, 3m is always 6+m and GF
\end{itemize}

\subsubsection{subseq after Gazzilli accepted}

16-21 pts is still wide, and as responder he will want to know the shape and at least a "cut" (ex: 19+ or not) for the opener if he has slam interest.
Here I proposed a simple method: exchange the lowest new suit with \texttt{2N}, showing a waiting hand, and after that, the responder can freely bids natrually at the two level or \texttt{2N} as a waiting bid.
This achieves a similar effect as 2-over-1 (i.e. after \texttt{1M - 2m}, \texttt{2M} is catchall, and then \texttt{2N} is another waiting; not waiting but bid in 3-level shows SI). The waiting bids are shown here:

\bin{\currfiledir/seq/Gaz_waiting}

\subsection{rebids}

Finally, I'm going to dive quickly into the most common responses of the opener's rebids: 

\subsection{1m - 1M}

\bin{\currfiledir/seq/1m-1M}

\subsection{1m - 1N \& 1C - 1S}

\bin{\currfiledir/seq/1m-1SN}

\subsection{1S - 1N \& 1H - 1SN}

\bin{\currfiledir/seq/1M-1N}

\subsection{2/1, and nebulous 2C}

We use the "2/1 always GF \& nebulous 2C" approach, where all balanced GF hands without 5D/H starts with 2C so that 2D/H promises 5+ card. (4441 usually starts with 2D, because its tolarable to bid D with a fit anyways)

For response to 2/1, I suggest slightly modified from the "2M default" system: (where extra = about a K more than the minimum)
\bin{\currfiledir/seq/note_2_over_1}

For subsequent sequences, here are the principles:
\bin{\currfiledir/seq/note_2_over_1_subseq}

\subsection{notes}

\subsubsection{after Gaz's weak 2m}

Although we say "same as natrual", but we shall clarify a bit:

\bin{\currfiledir/seq/note_1m}

\subsubsection{2-way}

\bin{\currfiledir/seq/note_2way}

\subsubsection{1m - 2N rebid}

\bin{\currfiledir/seq/note_2N}

\subsubsection{Jacoby 2N}

see {\color{blue} conventions/ST}

\subsubsection{minor invite}

We have many minor invites, no matter after 1m, 1M, or 1N. You expect partner to accept with:
not-too-bad 12 with Hx+ fit, or good 13 otherwise. 
That is, with honor support, you can accept with lighter hand compare to normal invite; otherwise, you should be sounder.
The reason is, with (22)23 points and 6-card running suit, 3N is very close. However, with one tempo missing, you'll have a harder time against good opponents. \\
The next question is, what should invitational hand's strength be: in my opinion, it should be:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item (9)10, or bad 11 points.
    \item can be lighter with 7+ suit
    \item must have good honors (roughly 2-of-top-3, or 3-of-top-5), but \textit{usually not solid}, since in this case opener would never have honors
\end{itemize}

\subsubsection{difficult sequences}

Here I list some sequences that is easily confused (as inv): 

\bin{\currfiledir/seq/note_confuse}
