\section{vs artificial bids}

To tackle those artificial bids' problem, we need classify them into:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item transfers: promising only 1 known (5+ cards) suit
    \item multi: promise 1 unknown suit
    \item assumed-fit: promises 0 or 2+ suits: take-out, Micheals, unusual, fertilizer, etc. 
    \item art fit
    \item multi-way bids that is not above 
\end{itemize}

Situations can also be classified into:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item opponents opened pre (or non-pre, ex: Flannery or precision 2D)
    \item we opened and are overcalled (since in this case partner has promised some strength)
\end{itemize}

\subsection{principles}

General principles are:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item advances are generally natrual if it's not opponents suit
    \item opponents 5+ card suit usually treated as cuebid (meaning might vary)
    \item if we opened NT, then transfer Leb applied
    \item P then bid shows a weaker hand. but P then X may vary.
    \item however, if we already have other methods, then use it (ex: supp X)
\end{itemize}

\subsection{vs transfers}

\begin{itemize}
    \setlength\itemsep{0pt}
    \item X = t/o and may be lighter than usual  (X then X: slightly stronger than usual)
    \item P then X = PEN if partner opened or they preempted. otherwise still t/o.
    \item P then bid = often lighter
    \item direct cuebid = same as original (usually: Micheals, or fit)
    \item others = same as original
\end{itemize}

Here are some common situations:

\bin{\currfiledir/seq/transfer}

\subsection{vs assumed-fit \& unusual}

We need to talk about penalty scheme first. When partner opens and opp uses multi or assumed-fit bids:
\begin{itemize}
    \setlength\itemsep{0pt}
    \item P then X = inv+, flat (bal) hand. partner can choose to defend or bid natrually
    \item X then P/X = PEN in at least one suit. usually sharper so subseq P implies t/o (opener's X is coop)
\end{itemize}

If they t/o or does not promises a 5-card suit, then we simply use system on, or natrual, or otherwise specified. (note: please check our defense to t/o)
Otherwise, we use unusual-vs-unusual:

\bin{\currfiledir/seq/UvU}

Here are some common situations:

\bin{\currfiledir/seq/afit}

\subsection{vs assumed-fit pres}

If they open preempt, we might need more case-by-case analysis.

\bin{\currfiledir/seq/afit_pre}

\subsection{vs multi}

Multi is hard to defend.

\bin{\currfiledir/seq/multi}

\subsection{vs art fit}

\bin{\currfiledir/seq/art_fit}

\subsection{vs other \& multi-way bids}

\bin{\currfiledir/seq/other}
