# same sequences
1M - 2X - 2N = 6+M without 4oM, any strength
1M - 2Y - 3X = nat extra
1M - 2X - 3Y = good 16+, 5-5 slamish
    # for above: bid natrually with fast arrival. reverses may just indicate strength.
1M - 2X - 3N = (15)16-18, exactly 5M332fit
    4X = SI, please RKC unless min
    4N = quant
    reverse = usually cue, fit in M, ST
    1S - 2H - 3N - 4C/D*= ST in H/S  # very hard to memorize!
    1M - 2D - 3N - 4C = natrual, 55, ST
    1H - 2D - 3N - 4S = RKC

# raises
1M - 2D - 3D = 4+ fit (not promising extra); or 3+ fit with extra
1S - 2H - 3H = 3+ fit, extra. 4H = 3+ fit, min.  # do we want to put this in 2S?
1M - 2C - 3C = 4+ fit, extra
    # for all above
    3N = min, s/o  # then 4m = MST, 4m+1 = RKC
    4m = mild slam inv
    3M = 3+ fit with mild extra, then  # +1 = FF as always
        [after C double fit] resp's next bid 4C shows real 5+ suit (not denying control under that), and therefore 4D = 2RKC. if unfortunately the sequence went 1M - 2C - 3C - 3M - 4C, then just 4M+1 RKC (giving up 2RKC), then optionally play in 6C instead.
        [after D/H double fit] 4H/4N is 2RKC.
    4M = dead min
    others = stopper-related, but can be cuebid before ST
    # cuebid first so that kickback RKC is clearer. jump new suit may be treated as auto-splinter

# side suit
1H - 2D - 2S = extra, or 6H4S
1S - 2D - 2H = always show 4H, not promising extra
1M - 2C - 2oM = always show 4oM, not promising extra
1M - 2C - 2M = extra with 4+D
    # for all above
    if 2M/oM is available: 2M/oM = fit, 3M/oM = almost slam-force. 4M/oM = min, picture bid
    if not: 3M/oM = extra. 4M/oM = min (fast arrival)
    2N = waiting bid
    4-th suit = weakish ask for stop (opener treated as this), or nat 65 and will promise rebid
    rebid 3m = 6+m, extra  # ?

# default bid
1M - 2DH - 2M = catchall: min unbal/bal, or rarely 19+ bal (will quant later)
    1H - 2D - 2H - 2S = nat, not promising extra
    2N = waiting and SI (or at least CoG), then bid natrually
    non-reverse 3X = nat 5-5 SI
    rebid = nat SI
    reverse 3X = weakish ask for stop (opener treated as this), or nat 65 and will promise rebid
    3N = to play
    3M = SI against min. 4M = to play (fast arrival)
1M - 2C - 2D = catchall: min unbal/bal (no 4oM), or 16-18 5M3fit32, or rarely 19+ bal (will quant later)
    2M = fit SI (not sure bal or not). 3M = almost slam-force. 4M = s/o
    2oM*= unbal-ish. may be asking for stopper or SI. then bid natrually.
    2N = bal-ish waiting and SI, then bid natrually
    rebid = nat SI
    reverse 3D = nat and SI
    reverse 3H = no agreement. maybe 65
    3N = to play

# responder's jump bid
# the following are auto-splinters, showing (15)16+ values and usually 4 but can be 3-fit
1M - 2DH - 2M - jump 
1M - 2C - 2D - jump
1M - 2X - 2N - jump
1M - 2X - 2oM - jump