\section{1X interfered}

Unless explicitly said "subseq ON", subseq is OFF.

\subsection{vs t/o}

Please notice that after XX, it is a FP (to 2N) scheme so that X is PEN.

\bin{\currfiledir/seq/takeout}

\subsection{vs 1-level overcall}

I've considered \textit{italian style}, but maybe later.

\bin{\currfiledir/seq/1X_overcall}

\subsection{vs 2-level overcall}

\bin{\currfiledir/seq/2X_overcall}

\subsection{the 2N raise}

In the following situations:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item partner opens or overcalls 1M (or non-jump 2M)
    \item is then overcalled < 2N (not doubled)
    \item (we are overcaller) the original mixed raise no longer exists. i.e. (1X) - 1M - (2X or higher)
\end{itemize}

\texttt{2N} is artificial and showing a raise. It shows:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item if this is the only raise under 3M (i.e. ... 1H/2H - (2S)), it shows inv+ raise
    \item otherwise, among 2N and cue, higher = mixed raise, lower = inv+ raise
\end{itemize}

We use the higher as mixed raise because it is semi-preemptive.

\subsubsection{mixed raise}

mixed raise, showing a less-then-inv constr 4+ fit. which means:
\begin{itemize}
    \setlength\itemsep{0pt}
    \item 9-11 for overcalling
    \item (7)8-9(10) for opening
\end{itemize}

\subsection{neg X and continuation}

As above, since we used \texttt{2N} artificially, we need to put bal inv into neg X. 
Specifically, neg X can contain:

\bin{\currfiledir/seq/negX}

For opener's rebid, some notes:

\begin{itemize}
    \setlength\itemsep{0pt}
    \item since there are too many non-default cases, don't jump to 4M with GF M fit unless there are no space. you should cuebid or X first.
    \item good-bad is ON if: \texttt{1S - (2H) - X}, or after negative X vs jump overcall
    \item otherwise, 2N shows extra and stoppers, 3X shows extra and no fit
    \item bid under 2M is natrual and usually not GF (but does not deny extra)
    \item 2M is default, i.e. does not promise extra length
\end{itemize}

\subsection{vs later overcalls}

Here are some general notes if overcalled in later auctions:

\bin{\currfiledir/seq/4_seat_general}

Some specific cases:

\bin{\currfiledir/seq/F1N_takeout}

\subsection{TBD}

just a quick note: if we are overcaller, then 
Rubens is ON if overcalls <= 2D, and is passed. (in this case, transfer from opp's suit)
Rubens is ON if overcalls 2m, and is doubled.
transfer from 1N if doubled: transfer to opp's suit shows 10+ and no fit.
either way, jump = fit-showing, about 9-11 values, jump cue = mixed raise, also 9-11 values
All other unmentioned cases, we bid natrually for now.
